\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{physics}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\relpenalty=10000
\binoppenalty=10000
\DeclareMathOperator{\lcm}{lcm}

\begin{document}	
\section*{Diophantine equations}
\begin{enumerate}
	\item 
	Diophantine equations are polynomial equations, usually in two or more unknowns, such that only integer solutions are sought.
	\item 
	A Diophantine equation equates two or more monomials, each of degree $1$ in one of the variables, to a constant.
	\item 
	An exponential Diophantine equation is one in which exponents on terms can be unknowns. 
\end{enumerate}
\section*{Problems}
\begin{enumerate}
	\item 
	Given integers $a,b,c$, find the conditions on $a,b,c$ such that there is an integer solution $x,y$ to
	$ax+by=c$.
	\item % andreescu 3.2.intro
	Prove that for every positive integer $m$ there is a positive integer $n$ such that $m+n+1$ is a perfect square and $mn+1$ is a perfect cube.
	
	\item % andreescu 3.2.intro
	Show that if $a,b$ are integers such that $\tfrac{a^2+b^2}{1+ab}$ is also an integer, then $\tfrac{a^2+b^2}{1+ab}$ is a perfect square.
	
	\item % aops
	Solve in integers
	$$x^3 +x^2 + x + 1 = y^2$$
	
	\item % andreescu 3.5.9
	Prove that the equation $y^2=x^5-4$ has no integer solutions.
	
	\item % stevens 4.2.3
	Prove that there are no integer solutions to
	$$x^3 + y^4 = 19^{19}$$
	
	\item % stevens 4.2.4
	Find all solutions to the equation $x^5 = y^2 + 4$ in positive integers.
	
	\item % andreescu 3.6.intro
	Find the positive integer solutions to the equation
	$3^x+4^y=5^z$	
	
	\item % andreescu 3.2.15
	Prove that if there exists a triple of positive integers $(x,y,z)$ such that 
	$$x^2 + y^2+1 = xyz$$
	then $z=3$ and find all such triplets.
	
	\item % andreescu 3.6.4.b
	Given an odd prime $p$, find all pairs of nonnegative integers $x,y$ that solve the equation
	$$p^x - y^p =1$$
	
\end{enumerate}


\end{document}